Exploration

### 2018-03-05 exploration.Rmd
credentials trigger

## Landscape
The landscape characteristics are aggregated here. It is a gridded landscape with climate and LULC data.
```{r landscape}
env.rct <- as.tibble(expand.grid(x=1:max(lc.df$x),
                                 y=1:max(lc.df$y))) %>%
  mutate(x_y=paste(x, y, sep="_")) %>%
  mutate(temp=c(scale(lc.df$bio1_mean))[match(.$x_y, lc.df$x_y)],
         temp2=temp^2,
         prec=c(scale(lc.df$bio12_mean))[match(.$x_y, lc.df$x_y)],
         prec2=prec^2,
         pOpn=lc.df$nlcd1_mean[match(.$x_y, lc.df$x_y)],
         pOth=lc.df$nlcd2_mean[match(.$x_y, lc.df$x_y)],
         pDec=lc.df$nlcd3_mean[match(.$x_y, lc.df$x_y)],
         pEvg=lc.df$nlcd4_mean[match(.$x_y, lc.df$x_y)],
         pMxd=lc.df$nlcd5_mean[match(.$x_y, lc.df$x_y)],
         inbd=!is.na(match(.$x_y, lc.df$x_y)),
         id=row_number(), 
         id.inbd=min_rank(na_if(inbd*id, 0)),
         lat=lc.df$top[match(.$x_y, lc.df$x_y)],
         lon=lc.df$left[match(.$x_y, lc.df$x_y)])
env.rct[is.na(env.rct)] <- 0
sdd.pr <- sdd_set_probs(ncell=n.cell, lc.df=env.rct, lc.col=8:12,
                        g.p=list(sdd.max=sp_i$p$sdd_max, 
                                 sdd.rate=sp_i$p$sdd_rate, 
                                 bird.hab=rep(1,5)))
env.df <- filter(env.rct, inbd) %>% select(4:12, 1:3, 13:17) %>%
  mutate(pOpn=c(scale(pOpn)), pOth=c(scale(pOth)), pDec=c(scale(pDec)),
         pEvg=c(scale(pEvg)), pMxd=c(scale(pMxd)))
rm(env.rct)
## sdd.pr[,,2,] has indexes based on env.df$id -- NOT env.df$id.inbd
# ggplot(env.df, aes(x=lon, y=lat, fill=id %in% sdd.pr[,,2,760])) + geom_tile()
```

>>>>

## Landscape
The landscape characteristics are aggregated here. It is a gridded landscape with climate and LULC data.
```{r landscape}
env.rct <- as.tibble(expand.grid(x=1:max(lc.df$x),
                                 y=1:max(lc.df$y))) %>%
  mutate(x_y=paste(x, y, sep="_")) %>%
  mutate(temp=c(scale(lc.df$bio1_mean))[match(.$x_y, lc.df$x_y)],
         temp2=temp^2,
         prec=c(scale(lc.df$bio12_mean))[match(.$x_y, lc.df$x_y)],
         prec2=prec^2,
         pOpn=lc.df$nlcd1_mean[match(.$x_y, lc.df$x_y)],
         pOth=lc.df$nlcd2_mean[match(.$x_y, lc.df$x_y)],
         pDec=lc.df$nlcd3_mean[match(.$x_y, lc.df$x_y)],
         pEvg=lc.df$nlcd4_mean[match(.$x_y, lc.df$x_y)],
         pMxd=lc.df$nlcd5_mean[match(.$x_y, lc.df$x_y)],
         inbd=!is.na(match(.$x_y, lc.df$x_y)),
         id=row_number(), 
         id.inbd=min_rank(na_if(inbd*id, 0)),
         lat=lc.df$top[match(.$x_y, lc.df$x_y)],
         lon=lc.df$left[match(.$x_y, lc.df$x_y)])
env.rct[is.na(env.rct)] <- 0
sdd.pr <- sdd_set_probs(ncell=n.cell, lc.df=env.rct, lc.col=8:12,
                        g.p=list(sdd.max=sp_i$p$sdd_max, 
                                 sdd.rate=sp_i$p$sdd_rate, 
                                 bird.hab=rep(1,5)))
env.df <- filter(env.rct, inbd) %>% select(4:12, 1:3, 13:17) %>%
  mutate(pOpn=c(scale(pOpn)), pOth=c(scale(pOth)), pDec=c(scale(pDec)),
         pEvg=c(scale(pEvg)), pMxd=c(scale(pMxd)))
rm(env.rct)
# sdd.pr[,,2,] has indexes based on env.df$id -- NOT env.df$id.inbd
# ggplot(env.df, aes(x=lon, y=lat, fill=id %in% sdd.pr[,,2,760])) + geom_tile()
```
